General purpose gene annotation using deep learning

### 2020-03-28 paper/main.tex
best animal model number in paper

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Augustus & 0.632 (+-0.089) & 0.749 (+-0.161)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  - (+-) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case.}
\end{table}

>>>>

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Augustus & 0.632 (+-0.089) & 0.749 (+-0.161)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  0.85 (+-0.068) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case.}
\end{table}
